Spatial Reasoning and Statistical Graphics

### 2014-10-11 Paper/Draft1/TestingVisualAptitude.Rnw
Fixing comments

\comment{The text makes still a lot of references to `preliminary results'. Don't just use copy \& paste for the changes!!!! Go through those sections and adjust. We are working on the final analysis now. Even if numbers might still change, they are not preliminary anymore. }
\section{Introduction}
Relevant literature: 
\begin{itemize}
\item \citet{shah1995conceptual} showed that spatial ability was not correlated with accuracy on a simple two-dimensional line graph description task, but that mathematical ability was correlated with accuracy. 
\item \citet{just1985cognitive} showed that high-spatial-ability viewers used different rotation strategies than low-spatial-ability viewers when asked to whether three-dimensional alphabet cubes were the same. 
\item \citet{hofmann2012graphical} for lineup stimuli and general lineup performance
\end{itemize}

@@

\begin{figure}[htbp]\centering
\includegraphics[width=0.75\textwidth]{fig-VisReasoningAnalysisCts}
\caption[Visual Aptitude Study Results]{Scatterplots of all test scores compared to participants' scores in the lineup tests. \comment{What is the main message of these plots? Relatively strong positive correlation to all established test scores?}}\label{fig:visualaptitudects}
\end{figure}

@@

\begin{figure}[htbp]\centering
\includegraphics[width=\textwidth]{fig-VisReasoningAnalysisCat}
\caption[Visual Aptitude Study Results]{Preliminary results of categorical variables compared to lineup score.}\label{fig:visualaptitudecat}
\end{figure}

>>>>

% \comment{The text makes still a lot of references to `preliminary results'. Don't just use copy \& paste for the changes!!!! Go through those sections and adjust. We are working on the final analysis now. Even if numbers might still change, they are not preliminary anymore. }
\section{Introduction}
Relevant literature: 
\begin{itemize}
\item \citet{shah1995conceptual} showed that spatial ability was not correlated with accuracy on a simple two-dimensional line graph description task, but that mathematical ability was correlated with accuracy. 
\item \citet{just1985cognitive} showed that high-spatial-ability viewers used different rotation strategies than low-spatial-ability viewers when asked to whether three-dimensional alphabet cubes were the same. 
\item \citet{hofmann2012graphical} for lineup stimuli and general lineup performance
\end{itemize}

@@

\begin{figure}[htbp]\centering
\includegraphics[width=0.75\textwidth]{fig-VisReasoningAnalysisCts}
\caption[Visual Aptitude Study Results]{Scatterplots of all test scores compared to participants' scores in the lineup tests. There is a relatively strong positive correlation between lineup score and scores on visuospatial reasoning tests.}\label{fig:visualaptitudects}
\end{figure}

@@

\begin{figure}[htbp]\centering
\includegraphics[width=\textwidth]{fig-VisReasoningAnalysisCat}
\caption[Visual Aptitude Study Results]{Demographic characteristics compared with lineup score.}\label{fig:visualaptitudecat}
\end{figure}
